### 2017-05-22 2017mergingmerges/section/02-Processes.tex
Fix phrasing in discussion of fusing cases

% -----------------------------------------------------------------------------
\subsubsection{Fusing Cases}
Once the result machine has arrived at the joint state @F3@, this is equivalent to the two source machines arriving in states @A1@ and @B1@ respectively. The lower half of Figure~\ref{fig:Fusion:Case} shows the next few transitions of the source machines. From state @A1@, the @group@ machine needs to perform a @case@ branch to determine whether to push the current value it has from its input stream @sIn1@ to output stream @sOut1@, or to just pull the next value from its input. From state @B1@, the @merge@ machine needs to pull a value from its second input stream @sIn2@. In the result machine, @F3@ performs the case analysis from @A1@, moving to either @A2@ or @A3@, corresponding to @F4@ and @F5@ respectively. From state @F4@, the push at @A2@ is executed and moves to @A3@, corresponding to @F5@. Finally, at @F5@ the @merge@ machine pulls from @sIn2@, moving from @B1@ to @C0@. Because the stream @sIn2@ is only pulled from by the @merge@ machine, no coordination is required between the @merge@ and @group@ machines for this pull.

>>>>

% -----------------------------------------------------------------------------
\subsubsection{Fusing Cases}
Once the result machine has arrived at the joint state @F3@, this is equivalent to the two source machines arriving in states @A1@ and @B1@ respectively. The lower half of Figure~\ref{fig:Fusion:Case} shows the next few transitions of the source machines. From state @A1@, the @group@ machine needs to perform a @case@ branch to determine whether to push the current value it has from its input stream @sIn1@ to output stream @sOut1@, or to just pull the next value from its input. From state @B1@, the @merge@ machine needs to pull a value from its second input stream @sIn2@. In the result machine, @F3@ performs the case analysis from @A1@, moving to either @F4@ or @F5@, corresponding to @A2@ and @A3@ respectively. From state @F4@, the push at @A2@ is executed and moves to @F5@, corresponding to @A3@. Finally, at @F5@ the @merge@ machine pulls from @sIn2@, moving from @F5@ to @F6@, corresponding to @B1@ and @C0@ respectively. As the stream @sIn2@ is only pulled from by the @merge@ machine, no coordination is required between the @merge@ and @group@ machines for this pull.
